\documentclass[]{report}
\usepackage{graphicx}	
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{subfiles}
\usepackage{geometry}
\usepackage{braket}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=cyan,      
    urlcolor=cyan,
    pdftitle={Phi Design},
}

\usepackage{listings}
\usepackage{xcolor}

\usepackage{arev}

\usepackage{fontspec}
    \setmainfont{SF Pro Text Regular}
    \setmonofont{Fira Mono}

\usepackage{titlesec}
\titleformat{\chapter}[display]
  {\normalfont\huge}
  {\bfseries\thechapter}{20pt}{\Huge}

\titleformat{\section}
    {\normalfont\Large}
    {\thesection}{1em}{}

\titleformat{\subsection}
    {\normalfont\itshape\large}
    {\thesubsection}{1em}{}

\definecolor{codegreen}{rgb}{0.3,0.3,0.3}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.69,0.69,0.69}
 
\lstdefinestyle{mystyle}{ 
    commentstyle=\color{codegreen},
    keywordstyle=\color{codegreen}\normalfont,
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,   
	tabsize=2,
    basicstyle=\ttfamily
}
 
\lstset{style=mystyle}


\usepackage{titling}
\renewcommand\maketitlehooka{\null\mbox{}\vfill}
\renewcommand\maketitlehookd{\vfill\null}

\title{\Huge \textbf{Robotics Exec Application}: Programming Officer}
\author{\LARGE Rishi Kothari, Grade 9, 684386}
\date{VEX Team, TFSS}

\geometry{margin=1in}

\begin{document}
\pagenumbering{gobble}
\maketitle
\newpage

\pagenumbering{arabic}

\chapter{Why I want the position}

Programming is something that I have enjoyed since I was in grade 3, but in recent years, I've started to notice that not many other people can enjoy that same experience. This is something that I find unsettling, and in that same time, I've made it my duty to make coding more accessible. In pursuit of this, I've joined Hack Club, created a Coding Club at my last school, and created an FLL team for the 2017-18 season. I've loved leading those clubs and seeing peoples' faces light up when they see what they built. As a result, I want to continue doing things like this, and I think that the best opportunity for me to do that in TFSS is by becoming the Programming Officer for the Robotics Team.

\chapter{Why you should pick me for this position}

Programming and Robotics are inseparable; neither would exist without the other. The Programming Officer needs to be well-balanced, in that they have both technical knowledge on both, as well as social knowledge, to moderate the people. In terms of technicality, I think that I have a very strong offering. Programming has been a very large passion of mine, and I've strived to be the best I possibly can be, by competing in various events and taking part in projects and internships. This year, my team had a very strong finish of 15th at UWaterloo's premier hackathon: Hack the North, where we built a budgeting app using Azure ML, Firebase, React.js, and Python. I'm also the lead Mobile Developer at TeamStudy, designing and building their app using SwiftUI, in addition to making the Phi language; Hoot-cli, a CLI assignment tracker; and Omega, my personal assistant. However, my strengths don't just lie in programming. It is essential for a programming officer to have knowledge of some robotics, which I feel that I also have. I've led my Davis Robotics team to 3rd place in FLL, and won the Programming award on the way, in addition to working with the VEX EDR platform and RobotC. Those robotics and coding experiences have given me a very strong sense of leadership and confidence in myself, and I truly think that I would be able to use them best as the Programming Officer for the TFSS Robotics team.

\chapter{A little bit more about me}
\textbf{Experience: } ~6 years
\\
\textbf{Languages: }
\begin{itemize}
    \item \textit{Functional:}
    \begin{itemize}
        \item Haskell
        \item Javascript
        \item Elm
        \item PureScript
        \item Python
    \end{itemize}
    \item \textit{OOP:}
    \begin{itemize}
        \item Swift
        \item C++
        \item Rust
        \item Go
    \end{itemize}
    \item \textit{Mathematical:}
    \begin{itemize}
        \item Phi (My own project)
        \item LaTeX (used to make this!)
    \end{itemize}
\end{itemize}

\textbf{Favourite Language: } Rust

\textbf{Repositories on Github: } 58

\textbf{2019 Internship: } Team Study as Mobile Developer

\textbf{Github: } \href{https://github.com/rishiosaur}{Github} https://github.com/rishiosaur

\textbf{Website: } \href{https://rishi.js.org}{Website} https://rishi.js.org


\end{document}  